
\chapter{Conclusion and outlook}
In this work, we explored the sensitivity of the production process of Higgs plus single top.
The $tH$ process is an interesting channel in proton-proton collisions in the LHC. This process has not been observed experimentally. Recently CMS published a search for $tH$ production using 35.9 fb$^{-1}$ from Run 2\cite{th1}. Using information from this publication, we studied the expected sensitivity using an Asimov data and systematic uncertainties for the final state with same sign pairs of muons. 

For an integrated luminosity of 35.9 fb$^{-1}$, we obtained an expected uncertainty for the $tH$ signal strength $\mu$ is around eight times than the value of $\mu$ for the SM. In this case, we estimated an upper limit on $\mu$ of 17 at 95$\%$ confidence level. 
For the inverted coupling scenario ($k_t$ =-1), the uncertainty after the fit was around 50$\%$, this is due to the larger expected number of signal events.

We also studied the sensitivity for larger integrated luminosity expected in future runs of the LHC. We find that for the SM scenario the expected uncertainty even at the largest integrated luminosity is not enough to observe the signal and only an upper limit on $\mu$ is placed at 4.3. In the case of the inverted coupling scenario, a possible signal can be observed with an uncertainty of 10$\%$ at 3000 fb$^{-1}$.

However, these results use only the dimuon channel, the sensitivity can be improved by combining more search channels. The search can include additional channels, such as three lepton in the final state or Higgs decays to a pair of photons. By adding more channels, the number of events increases and can give us better statistics. 


 %Alternatively, this scenario will be ruled out. For  3000 fb$^{-1}$, the statistical test shows that the model of $k_t$=-1 can be rule out. 

%In the SM, same sign $\mu\mu$ final states of the $tH$ process, it shows that is impossible to give evidence of the existence of a Higgs boson due to high uncertainties. The expected uncertainty even at the largest luminosities is not enough to observe the signal and only an upper limit can be placed. 
%For the $k_t$=-1, the uncertainty is low due to higher number of events for tH process and it is possible to give evidence of a Higgs
%boson, but this model is purely theoretical.\\

